\thetitle

### 2021-03-02 writing/rational-methodology.tex
adding methodology subsection

Each time the rational programmer debugs a program, it is
validation for programming languages researchers; their blame assignment 
mechanisms provide information that points towards the source of the
problem. Moroeover, their slogans and theorems help programmers connect the dots.
In contrast, when the rational programmer fails, it speaks for the
limited predictive power of programming languages theory and the
misleading projections of language design.

In other words the rational programmer implies a methodology for
evaluating
the design of programming lanaguages features such as blame assignment mechanisms. 
In general terms, the methodology consists of four 
pieces:

@@

\item The evaluation of a blame assignment mechanism based on whtehr the
  information it provides was critical for the outcome of the experiment   
\end{itemize}

>>>>

Each time the rational programmer debugs a program, it is
validation for programming languages researchers; their blame assignment 
mechanisms provide information that points towards the source of the
problem. Moreover, their slogans and theorems help programmers connect the dots.
In contrast, when the rational programmer fails, it speaks for the
limited predictive power of programming languages theory and the
misleading projections of language design.

In other words the rational programmer implies a methodology for
evaluating
the design of programming languages features such as blame assignment mechanisms. 
In general terms, the methodology consists of four 
pieces:

@@

\item The evaluation of a blame assignment mechanism based on whether the
  information it provides was critical for the outcome of the experiment   
\end{itemize}
